---
title: "WCC City Highways: EV Charge Points"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    logo: www/logo.png
    favicon: www/logo.png
    css: styles.css
---

```{r setup, include=FALSE}
library(flexdashboard)
library(leaflet)
library(leaflet.extras)
library(leaflet.extras2)
library(sf)
library(readr)
library(dplyr)
library(lubridate)
library(DT)
library(rvest)
library(readxl)
library(stringr)
library(tidyr)
library(crosstalk)
```


```{r}
source("../concat_data.R")
west_bord=read_sf("../../../data/clean_data_files/westminster_boundary_files/westminster_border.json")

# full_points %>%
#   bind_cols(as_tibble(st_coordinates(full_points))) %>% rename("lon"="X", "lat"="Y") %>% 
#   as.data.frame() %>%
#   select(-geometry)

sd <- SharedData$new(full_points)
```

Map {data-icon="glyphicon-flash"}
=======================================================================

Inputs {.sidebar}
-------------------------------------

#### Filters

```{r}
filter_select("prov", "Providers", sd, ~Provider)
filter_checkbox("status", "Status", sd, ~Status)
filter_checkbox("bayType", "Bay Type", sd, ~IsDedicated)
filter_select("speed", "Speed", sd, ~Speed)
filter_slider("bays", "Number of Bays", sd, ~NoBays)
```

<div style="color:#1a242f">
<details>
  <summary>Additional Options</summary>
```{r}
filter_select("carclub", "Car Club", sd, c("To be added..."))
filter_select("public", "Restrictions", sd, c("To be added..."))
```
</details>
</div>

<br></br>
<hr></hr>
<br></br>

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A {.no-title .no-padding}


```{r}
# Totals and Summary Statistics
# Installs

lccp_pending <- dplyr::filter(full_points, Provider=="Ubitricity" & Status == "Pending Installation") %>% pull(NoBays) %>% sum()
lccp_existing <- dplyr::filter(full_points, Provider=="Ubitricity" & Status == "Installed") %>% pull(NoBays) %>% sum()

rapid_pending <- nrow(dplyr::filter(full_points, Provider=="ESB" & Status == "Pending Installation"))
rapid_existing <- dplyr::filter(full_points, Provider=="ESB" & Status == "Installed") %>% pull(NoBays) %>% sum()

ded_pending <- dplyr::filter(full_points, !Provider %in% c("ESB", "Ubitricity") & Status == "Pending Installation") %>% pull(NoBays) %>% sum()
ded_existing <- dplyr::filter(full_points, !Provider %in% c("ESB", "Ubitricity") & Status == "Installed") %>% pull(NoBays) %>% sum()

total_bays <- dplyr::filter(full_points, Status == "Installed") %>% pull(NoBays) %>% sum()

```

```{r}
addLegendCustom <- function(map, colors, labels, sizes, opacity = 1){
  colorAdditions <- paste0(colors, "; width:", sizes, "px; height:", sizes, "px")
  labelAdditions <- paste0("<div style='display: inline-block;height: ", sizes, "px;margin-top: 4px;line-height: ", sizes, "px;'>", labels, "</div>")

  return(addLegend(map, colors = colorAdditions, labels = labelAdditions, opacity = opacity))
}

leaflet() %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
    fitBounds(-0.18, 51.495, -0.13, 51.528) %>%
  #addPolygons(data=ward_bord, fill=F, fillOpacity = 0.3, opacity = 1, fillColor = "white", weight = 0.2, color = "black", label=~NAME, popup = ~paste(HECTARES, "Hectares")) %>%
  addPolygons(data=west_bord, fill=F, fillOpacity = 0.3, opacity = 1, fillColor = "white", weight = 1, color = "black") %>%
  addCircles(data=sd, weight=0, radius=~Radius, fillOpacity = ~Opacity, fillColor = ~Colour, group=~Group, label=~Provider, popup=~labs) %>%
  #addCircles(data=lccp, weight=0, radius=10, fillOpacity = 1, fillColor = "green", group="Lamp Column", label=~ChargepointID, popup=~labs) %>%
  #addCircles(data=future_lccp, weight=0, radius=10, fillOpacity = 0.5, fillColor = "green", group="Planned Lamp Column Charge Points", label="Confirmed Install", popup=~labs) %>%
  addReachability(apikey = "5b3ce3597851110001cf6248b97cbf2e9add4a2b953f36b5e27ddf4c",
                  options = reachabilityOptions(styleFn = list(fillOpacity=0.1, weight=1, fillColor="red"),
                                                expandButtonContent='',
                                                expandButtonStyleClass= 'reachability-control-expand-button fa fa-bullseye',
                                                drawButtonContent= '',
                                                drawButtonStyleClass= 'fa fa-pencil fa-2x',
                                                deleteButtonContent= '',
                                                deleteButtonStyleClass= 'fa fa-trash fa-2x',
                                                distanceButtonContent = '',
                                                distanceButtonStyleClass= 'fa fa-road fa-2x',
                                                timeButtonContent= '',
                                                timeButtonStyleClass= 'fa fa-clock-o fa-2x',
                                                travelModeButton1Content= '',
                                                travelModeButton1StyleClass= 'fa fa-car fa-2x',
                                                travelModeButton2Content= '',
                                                travelModeButton2StyleClass= 'fa fa-bicycle fa-2x',
                                                travelModeButton3Content= '',
                                                travelModeButton3StyleClass= 'fa fa-walking fa-2x',
                                                travelModeButton4Content= '',
                                                travelModeButton4StyleClass= 'fa fa-wheelchair-alt fa-2x',
                                                #rangeControlTime = c(3,5,7,10,15,20,30),
                                                markerFn = JS("function(latLng, travelMode, rangeType) {
                return L.circleMarker(latLng, { radius: 2, weight: 1, color: 'black', fillColor: 'black', fillOpacity: 1 });
            }")
                                                )) %>%
  addLegendCustom(colors = c("green", "#7DBF7A", "blue", "purple", "cyan"), labels = c("Lamp Column Charge Point (5kW)", "Planned Lamp Column Charge Point", "Dedicated Fast Charger (7-22kW)",  "Rapid Charge Point (50kW)", "Planned Rapid Charge Point"), sizes = c(15, 15, 20, 25, 25)) %>%
  addLegend(position="bottomright", labels = c("WCC - Charge Point Target: 1000", paste("Installed Bays:", total_bays), htmltools::HTML(paste('<label for="file">',round(total_bays*100/1000, 2) ,'% </label><progress id="file" value="',round(total_bays*100/1000, 2),'" max="100">',round(total_bays*100/1000, 2),'% </progress>', sep=""))), 
                                               values="d", colors = rep("black", 3), title="Westminster Wide Summary:") %>%
  addLegend(position="bottomright", labels = c(paste("Lamp Column Charge Points:", lccp_pending), 
                                                   paste("Rapid Charge Points: ", 17)), 
                                               values="d", colors = rep("black", 2), title="Pending Installation:") %>%
  addLegend(position="bottomright", labels = c(paste("Lamp Column Charge Points:", lccp_existing), 
                                                   paste("Dedicated Charge Point Bays:", ded_existing),
                                                   paste("Rapid Bays:", rapid_existing)), 
                                               values="d", colors = rep("black", 3), title="Installed:") %>%
  addSearchOSM() %>%
  addScaleBar(position="bottomleft")

```



```{r}
wards_polygon <- read_sf("../../../data/clean_data_files/westminster_boundary_files/London-wards-2018/London-wards-2018_ESRI/London_Ward.shp")
wards_polygon <- wards_polygon %>% dplyr::filter(DISTRICT == "City of Westminster") %>% st_transform(4326)
ward_names <- sort(wards_polygon$NAME)
```


```{r}
requests_ward <- read.csv("../../../data/clean_data_files/requests/ward_summary.csv")

plot_map <- function(ward){
  ward_polygon <- wards_polygon %>% dplyr::filter(NAME %in% ward) 

  ward_points <- full_points %>%
    dplyr::filter(Ward==ward)
  
  # Stats
  requests_ward <- requests_ward %>% filter(NAME == ward) %>% pull(n)
  
  lccp_pending <- nrow(dplyr::filter(ward_points, Provider=="Ubitricity" & Status == "Pending Installation"))
  lccp_existing <- nrow(dplyr::filter(ward_points, Provider=="Ubitricity" & Status == "Installed"))
  
  rapid_pending <- nrow(dplyr::filter(ward_points, Provider=="ESB" & Status == "Pending Installation"))
  rapid_existing <- nrow(dplyr::filter(ward_points, Provider=="ESB" & Status == "Installed"))
  
  ded_pending <- nrow(dplyr::filter(ward_points, !Provider %in% c("ESB", "Ubitricity") & Status == "Pending Installation"))
  ded_existing <- nrow(dplyr::filter(ward_points, !Provider %in% c("ESB", "Ubitricity") & Status == "Installed"))
  

leaflet() %>%
    addProviderTiles(providers$CartoDB.Positron) %>%
    addPolygons(data=ward_polygon, fillOpacity = 0, weight = 1, color = "black", opacity = 1) %>%
    addCircles(data=ward_points, stroke = FALSE, fillColor = ~Colour, fillOpacity = ~Opacity, label=~ChargepointID, radius = ~Radius, group = ~Group, popup=~labs) %>%
    #addCircles(data=dedicated_ward, lat=~Latitude, lng = ~Longitude, stroke = FALSE, fillColor = "blue", fillOpacity = 1, label = ~LocationName, radius = 15, group = "Dedicated Charge Point Bays", popup=~labs) %>%
    #addCircles(data=future_lccp_ward, lng=~lon, lat=~lat, stroke = FALSE, fillColor = "green", fillOpacity = 0.5, label = ~str_to_title(ChargepointID), radius = 8, group = "2020 Roll Out - Lamp Column Charge Points") %>%
    #addCircles(data=round2, lat=~Latitude, lng = ~Longitude, stroke = FALSE, fillColor = "cyan", fillOpacity = 1, label = ~Location, radius = 15, group = "Rapid Installations - Round 2") %>%
    #addCircles(data=round3, lat=~Latitude, lng = ~Longitude, stroke = FALSE, fillColor = "cyan", fillOpacity = 1, label = ~Location, radius = 15, group = "Rapid Installations - Round 3") %>%
    addLegend(position="bottomright", labels = c(paste("Lamp Column Charge Points:", lccp_existing), 
                                                 paste("Dedicated Charge Point Bays:", ded_existing), 
                                                 paste("Requests:", requests_ward),
                                                 paste("Lamp Columns in 2020 Roll Out:", lccp_pending),
                                                 paste("Planned Rapid Installations:", rapid_pending)), values="d", colors = rep("black", 5), title="Number of:") %>%
    addLegendCustom(colors = c("green", "#7DBF7A", "blue", "purple", "cyan"), labels = c("Lamp Column Charge Points", "Planned Lamp Column Charge Points", "Dedicated Charge Point Bays", "Rapid Charge Point",  "Rapid Installations"), sizes = c(15, 15, 20, 20, 20))# %>%
    #addLayersControl(overlayGroups = c("Lamp Column Charge Points", "Dedicated Charge Point Bays", "2020 Roll Out - Lamp Column Charge Points", "Rapid Installations - Round 2", "Rapid Installations - Round 3"),
      #position="bottomleft", options = layersControlOptions(collapsed = FALSE, autoZIndex = TRUE))
      
}


```


```{r}

out <- lapply(seq_along(ward_names), function(i) {

  a1 <- knitr::knit_expand(text = sprintf("\n%s {data-navmenu=\"Wards\" data-icon=\"fa-bars\"}", ward_names[[i]])) # tab header, auto extracts names of `hcs`
  a2 <- knitr::knit_expand(text = sprintf("\n=====================================\n"))
  a3 <- knitr::knit_expand(text = sprintf("\n### %s {.no-padding}\n", ward_names[[i]]))
  a4 <- knitr::knit_expand(text = "\n```{r}") # start r chunk
  a5 <- knitr::knit_expand(text = sprintf("\nplot_map(\"%s\")\n", ward_names[[i]])) # extract graphs by "writing" out `hcs[[1]]`, `hcs[[2]]` etc. to be rendered later
  a6 <- knitr::knit_expand(text = "\n```\n") # end r chunk

  paste(a1, a2, a3, a4, a5, a6, collapse = '\n') # collapse together all lines with newline separator

})
cat("\n")
cat("\n")
```

`r paste(knitr::knit(text = paste(out, collapse = '\n')))`

Department for Transport {data-navmenu="Open Data" data-icon="fa-bars"}
=======================================================================

Inputs {.sidebar}
-------------------------------------

All data and visualisations on this page were compiled by the DfT and can found on their website here: http://maps.dft.gov.uk/ev-charging-map/ 

Column {data-width=600}
-------------------------------------

### Datatable {data-width=300 .no-title}

```{r}
website <- read_html("http://maps.dft.gov.uk/ev-charging-map/")
tab <- website %>%
    html_nodes(css = "table") %>%
    .[[1]] %>%
    html_table()

boroughs <- read_sf("../../../data/clean_data_files/westminster_boundary_files/Local_Authority_Districts__December_2019__Boundaries_UK_BFE-shp/Local_Authority_Districts__December_2019__Boundaries_UK_BFE.shp")

boroughs <- boroughs %>% st_simplify(dTolerance = 500) %>% st_transform(4326)

boroughs <- boroughs %>%
  dplyr::left_join(tab, by=c("LAD19CD" = "ONS code")) %>%
  select(LAD19CD, `Local Authority`, `Total public charging devices`, `Total public rapid charging devices`, `Charging devices per 100,000 population`)

buckinghamshire <- boroughs %>% filter(is.na(`Local Authority`)) %>% st_union() 
buckinghamshire <- st_multipolygon(lapply(buckinghamshire, function(x) x[1])) %>% st_cast("POLYGON") %>% st_sfc()
buckinghamshire <- data.frame(a=c("E06000060"), b=c("Buckinghamshire"), c=c(135), d=c(22), e=c(25), f=c(buckinghamshire))
colnames(buckinghamshire) <- colnames(boroughs)

boroughs$`Total public charging devices` <- as.integer(boroughs$`Total public charging devices`)
boroughs$`Total public rapid charging devices` <- as.integer(boroughs$`Total public rapid charging devices`)
boroughs$`Charging devices per 100,000 population` <- as.integer(boroughs$`Charging devices per 100,000 population`)

boroughs <- bind_rows(boroughs, buckinghamshire) %>%
  dplyr::filter(!is.na(`Local Authority`))

DT::datatable(boroughs %>% data.frame(check.names = F) %>% select(-geometry), options = list(pageLength=nrow(boroughs), info = FALSE, dom="ft"))
```

Column {data-width=600}
-------------------------------------

### Datatable {data-width=700 .no-padding .no-title}

```{r}


binpal1 <- colorQuantile("YlGnBu", boroughs$`Total public charging devices`, 5)
binpal2 <- colorQuantile("YlGnBu", boroughs$`Total public rapid charging devices`, 5)
binpal3 <- colorQuantile("YlGnBu", boroughs$`Charging devices per 100,000 population`, 5)

boroughs %>%
  leaflet() %>% 
  setView(lat= 54.563652,lng= -5.067734, zoom=6) %>%
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addPolygons(weight=1, color = "white", fillOpacity=0.8, fillColor = ~binpal1(`Total public charging devices`), group="Total CP", popup=~`Local Authority`) %>%
  addPolygons(weight=1, color = "white", fillOpacity=0.8, fillColor = ~binpal2(`Total public rapid charging devices`), group="Total Rapid CP") %>%
  addPolygons(weight=1, color = "white", fillOpacity=0.8, fillColor = ~binpal3(`Charging devices per 100,000 population`), group="Total per Capita") %>%
  addLayersControl(baseGroups=c("Total CP", "Total Rapid CP", "Total per Capita"), layersControlOptions(collapsed=F))

```


About {data-icon="fa-bars"}
===================================== 

#### Westminster City Council EV Report

* **Date Created:** 2020-09-23
* **Date Updated:** `r today()`
* **Created By:** Westminster City Highways

This report shows the current and planned EV charge points in Westminster.






