---
title: "WCC: EV Charge Points"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    logo: www/logo.png
    favicon: www/logo.png
    css: styles.css
    social: [ "twitter", "facebook", "linkedin" ]
---

```{r setup, include=FALSE}
library(flexdashboard)
library(leaflet)
library(leaflet.extras)
library(leaflet.extras2)
library(sf)
library(readr)
library(dplyr)
library(lubridate)
library(DT)
library(rvest)
library(readxl)
library(stringr)
```

```{r ward_bord}
ward_bord <- sf::read_sf("../../../data/clean_data_files/westminster_boundary_files/London-wards-2018/London-wards-2018_ESRI/London_Ward_CityMerged.shp")
ward_bord <- st_transform(ward_bord, 4326) 
ward_bord <- ward_bord %>%
  dplyr::filter(DISTRICT == "City of Westminster")
```

```{r}
west_bord <- read_sf("../../../data/clean_data_files/westminster_boundary_files/westminster_border.json")

cp <- read_csv("../../../data/clean_data_files/usage_data/full_usage_data.csv")
cp <- cp %>%
  select(Latitude, Longitude, Provider) %>%
  unique() %>%
  mutate(colour = ifelse(Provider=="Ubitricity", "green", "blue")) %>%
  mutate(colour = ifelse(Provider=="ESB", "purple", colour)) %>%
  mutate(ChargeType = ifelse(Provider=="Ubitricity", "Lamp Column", "Dedicated")) %>%
  mutate(ChargeType = ifelse(Provider=="ESB", "Rapid", ChargeType)) 
```


Map {data-icon="glyphicon-flash"}
=======================================================================

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A {.no-title .no-padding}

```{r}
leaflet() %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  #fitBounds(-0.18, 51.495, -0.13, 51.528) %>%
  #addPolygons(data=ward_bord, fill=F, fillOpacity = 0.3, opacity = 1, fillColor = "white", weight = 0.2, color = "black", label=~NAME, popup = ~paste(HECTARES, "Hectares")) %>%
  addPolygons(data=west_bord, fill=F, fillOpacity = 0.3, opacity = 1, fillColor = "white", weight = 1, color = "black") %>%
  addCircles(data=cp, weight=0, radius=10, fillOpacity = 1, fillColor = ~colour, group=~ChargeType, label=~Provider) %>%
  addReachability(apikey = "5b3ce3597851110001cf62484c75d3ed4e8f4fab81992f9f4d2b83e6",
                  options = reachabilityOptions(styleFn = list(fillOpacity=0.1, weight=1, fillColor="red"),
                                                expandButtonContent='',
                                                expandButtonStyleClass= 'reachability-control-expand-button fa fa-bullseye',
                                                drawButtonContent= '',
                                                drawButtonStyleClass= 'fa fa-pencil fa-2x',
                                                deleteButtonContent= '',
                                                deleteButtonStyleClass= 'fa fa-trash fa-2x',
                                                distanceButtonContent = '',
                                                distanceButtonStyleClass= 'fa fa-road fa-2x',
                                                timeButtonContent= '',
                                                timeButtonStyleClass= 'fa fa-clock-o fa-2x',
                                                travelModeButton1Content= '',
                                                travelModeButton1StyleClass= 'fa fa-car fa-2x',
                                                travelModeButton2Content= '',
                                                travelModeButton2StyleClass= 'fa fa-bicycle fa-2x',
                                                travelModeButton3Content= '',
                                                travelModeButton3StyleClass= 'fa fa-walking fa-2x',
                                                travelModeButton4Content= '',
                                                travelModeButton4StyleClass= 'fa fa-wheelchair-alt fa-2x',
                                                #rangeControlTime = c(3,5,7,10,15,20,30),
                                                markerFn = JS("function(latLng, travelMode, rangeType) {
                return L.circleMarker(latLng, { radius: 2, weight: 1, color: 'black', fillColor: 'black', fillOpacity: 1 });
            }")
                                                )) %>%
  addLayersControl(overlayGroups = c("Lamp Column", "Dedicated", "Rapid")) %>%
  addSearchOSM() %>%
  addScaleBar(position="bottomleft")

```


```{r}
wards_polygon <- read_sf("../../../data/clean_data_files/westminster_boundary_files/London-wards-2018/London-wards-2018_ESRI/London_Ward.shp")
wards_polygon <- wards_polygon %>% dplyr::filter(DISTRICT == "City of Westminster") %>% st_transform(4326)
ward_names <- sort(wards_polygon$NAME)
```


```{r}
lccp <- read.csv("../../../data/clean_data_files/lamp_columns/lccp.csv") 
lccp <- lccp %>% dplyr::filter(easting > 200000)
lccp <- st_as_sf(lccp, coords = c("easting", "northing"), crs = "epsg:27700") %>% st_transform(4326)

dedicated <- read.csv("../../../data/clean_data_files/usage_data/full_usage_dedicated.csv")
dedicated <- dedicated %>%
  dplyr::select(LocationName, NoBays,Latitude,Longitude, Provider) %>%
  distinct()
dedicated$labs <- sapply(seq(nrow(dedicated)), function(i) {
    paste0( '<p><strong>Location: </strong>', 
            dedicated[i, "LocationName"],'</p><p><strong>Number of Bays: </strong>', 
            dedicated[i, "NoBays"],'</p><p><strong>Provider: </strong>',
            dedicated[i, "Provider"],'</p>') 
})
dedicated <- st_as_sf(dedicated, coords = c("Longitude", "Latitude"), crs = "epsg:4326", remove=FALSE)

rapid_roll_out <- read.csv("../../../data/clean_data_files/usage_data/rapid_roll_out_locations.csv")
rapid_roll_out <- st_as_sf(rapid_roll_out, coords = c("Longitude", "Latitude"), crs = "epsg:4326", remove=FALSE)

future_lccp <- read_excel("../../../analysis_requests/2020:08:18_SiemensDesktopReviewProgress/2020 - 09 - 15 - LCCP Proposed installation Listing - Complete.xlsx")
future_lccp <- future_lccp %>% dplyr::filter(`WCC Comments` == "Progress to next phase of site survey")
future_lccp <- st_as_sf(future_lccp, coords = c("easting", "northing"), crs = 27700, remove=FALSE) %>% st_transform(4326) 

requests_ward <- read.csv("../../../data/clean_data_files/requests/ward_summary.csv")

addLegendCustom <- function(map, colors, labels, sizes, opacity = 1){
  colorAdditions <- paste0(colors, "; width:", sizes, "px; height:", sizes, "px")
  labelAdditions <- paste0("<div style='display: inline-block;height: ", sizes, "px;margin-top: 4px;line-height: ", sizes, "px;'>", labels, "</div>")

  return(addLegend(map, colors = colorAdditions, labels = labelAdditions, opacity = opacity))
}

plot_map <- function(ward){
  ward_polygon <- wards_polygon %>% dplyr::filter(NAME %in% ward) 
  
  lccp_ward <- st_join(lccp, wards_polygon, join=st_within) %>%
    dplyr::filter(NAME %in% ward) %>%
    mutate(lon = purrr::map_dbl(geometry, function(x) x[1])) %>%
    mutate(lat = purrr::map_dbl(geometry, function(x) x[2]))
  lccp_ward[nrow(lccp_ward)+1,] <- NA
    
  # Dedicated Bays
  dedicated_ward <- st_join(dedicated, st_transform(wards_polygon, crs = "epsg:4326"), join=st_within) %>%
    dplyr::filter(NAME %in% ward)
  dedicated_ward[nrow(dedicated_ward)+1,] <- NA
  
  # Rapids Roll Out
  rapid_roll_out_ward <- st_join(rapid_roll_out, st_transform(wards_polygon, crs = "epsg:4326"), join=st_within) %>%
    dplyr::filter(NAME %in% ward)
  round2 <- rapid_roll_out_ward %>% dplyr::filter(Round==2)
  round2[nrow(round2)+1,] <- NA
  round3 <- rapid_roll_out_ward %>% dplyr::filter(Round==3)
  round3[nrow(round3)+1,] <- NA
  
  # Future LCCP
  future_lccp_ward <- st_join(future_lccp, st_transform(wards_polygon, crs = "epsg:4326"), join=st_within) %>%
    dplyr::filter(NAME %in% ward) %>%
    mutate(lon = purrr::map_dbl(geometry, function(x) x[1])) %>%
    mutate(lat = purrr::map_dbl(geometry, function(x) x[2]))
  
  future_lccp_ward[nrow(future_lccp_ward)+1,] <- NA
  
  # Requests
  requests_ward <- requests_ward %>% filter(NAME == ward) %>% pull(n)
  
  lccp_ward %>%
    leaflet() %>%
    addProviderTiles(providers$CartoDB.Positron) %>%
    addPolygons(data=ward_polygon, fillOpacity = 0, weight = 1, color = "black", opacity = 1) %>%
    addCircles(lat=~lat, lng = ~lon, stroke = FALSE, fillColor = "blue", fillOpacity = 1, label=~str_to_title(site_name), radius = 8, group = "Lamp Column Charge Points") %>%
    addCircles(data=dedicated_ward, lat=~Latitude, lng = ~Longitude, stroke = FALSE, fillColor = "red", fillOpacity = 1, label = ~LocationName, radius = 15, group = "Dedicated Charge Point Bays", popup=~labs) %>%
    addCircles(data=future_lccp_ward, lng=~lon, lat=~lat, stroke = FALSE, fillColor = "orange", fillOpacity = 1, label = ~str_to_title(site_name), radius = 8, group = "2020 Roll Out - Lamp Column Charge Points") %>%
    addCircles(data=round2, lat=~Latitude, lng = ~Longitude, stroke = FALSE, fillColor = "cyan", fillOpacity = 1, label = ~Location, radius = 15, group = "Rapid Installations - Round 2") %>%
    addCircles(data=round3, lat=~Latitude, lng = ~Longitude, stroke = FALSE, fillColor = "cyan", fillOpacity = 1, label = ~Location, radius = 15, group = "Rapid Installations - Round 3") %>%
    addLegend(position="bottomright", labels = c(paste("Lamp Column Charge Points:", sum(!is.na(lccp_ward$site_code))), 
                                                 paste("Dedicated Charge Point Bays:", sum(dedicated_ward$NoBays, na.rm = TRUE)), 
                                                 paste("Requests:", requests_ward),
                                                 paste("Lamp Columns in 2020 Roll Out:", sum(!is.na(future_lccp_ward$site_code))),
                                                 paste("Planned Rapid Installations: Round 2:", nrow(rapid_roll_out_ward%>%dplyr::filter(Round==2))),
                                                 paste("Planned Rapid Installations: Round 3:", nrow(rapid_roll_out_ward%>%dplyr::filter(Round==3)))), values="d", colors = rep("black", 6), title="Number of:") %>%
    addLegendCustom(colors = c("blue", "red", "orange", "cyan"), labels = c("Lamp Column Charge Points", "Dedicated Charge Point Bays", "2020 Roll Out - Lamp Column Charge Points (Subject to Survey)", "Rapid Installations (Subject to Survey)"), sizes = c(15, 20, 15, 20)) %>%
    addLayersControl(overlayGroups = c("Lamp Column Charge Points", "Dedicated Charge Point Bays", "2020 Roll Out - Lamp Column Charge Points", "Rapid Installations - Round 2", "Rapid Installations - Round 3"),
      position="bottomleft", options = layersControlOptions(collapsed = FALSE, autoZIndex = TRUE))
      
}


```


```{r}

out <- lapply(seq_along(ward_names), function(i) {

  a1 <- knitr::knit_expand(text = sprintf("\n%s {data-navmenu=\"Wards\" data-icon=\"fa-bars\"}", ward_names[[i]])) # tab header, auto extracts names of `hcs`
  a2 <- knitr::knit_expand(text = sprintf("\n=====================================\n"))
  a3 <- knitr::knit_expand(text = sprintf("\n### %s {.no-padding}\n", ward_names[[i]]))
  a4 <- knitr::knit_expand(text = "\n```{r}") # start r chunk
  a5 <- knitr::knit_expand(text = sprintf("\nplot_map(\"%s\")\n", ward_names[[i]])) # extract graphs by "writing" out `hcs[[1]]`, `hcs[[2]]` etc. to be rendered later
  a6 <- knitr::knit_expand(text = "\n```\n") # end r chunk

  paste(a1, a2, a3, a4, a5, a6, collapse = '\n') # collapse together all lines with newline separator

})
cat("\n")
cat("\n")
```

`r paste(knitr::knit(text = paste(out, collapse = '\n')))`

DfT
=======================================================================


Inputs {.sidebar}
-------------------------------------

All data and visualisations on this page were compiled by the DfT and can found on their website here: http://maps.dft.gov.uk/ev-charging-map/ 

Column {data-width=600}
-------------------------------------

### Datatable {data-width=300 .no-title}

```{r}
website <- read_html("http://maps.dft.gov.uk/ev-charging-map/")
tab <- website %>%
    html_nodes(css = "table") %>%
    .[[1]] %>%
    html_table()

boroughs <- read_sf("../../../data/clean_data_files/westminster_boundary_files/Local_Authority_Districts__December_2019__Boundaries_UK_BFE-shp/Local_Authority_Districts__December_2019__Boundaries_UK_BFE.shp")

boroughs <- boroughs %>% st_simplify(dTolerance = 500) %>% st_transform(4326)

boroughs <- boroughs %>%
  dplyr::left_join(tab, by=c("LAD19CD" = "ONS code")) %>%
  select(LAD19CD, `Local Authority`, `Total public charging devices`, `Total public rapid charging devices`, `Charging devices per 100,000 population`)

buckinghamshire <- boroughs %>% filter(is.na(`Local Authority`)) %>% st_union() 
buckinghamshire <- st_multipolygon(lapply(buckinghamshire, function(x) x[1])) %>% st_cast("POLYGON") %>% st_sfc()
buckinghamshire <- data.frame(a=c("E06000060"), b=c("Buckinghamshire"), c=c(135), d=c(22), e=c(25), f=c(buckinghamshire))
colnames(buckinghamshire) <- colnames(boroughs)

boroughs$`Total public charging devices` <- as.integer(boroughs$`Total public charging devices`)
boroughs$`Total public rapid charging devices` <- as.integer(boroughs$`Total public rapid charging devices`)
boroughs$`Charging devices per 100,000 population` <- as.integer(boroughs$`Charging devices per 100,000 population`)

boroughs <- bind_rows(boroughs, buckinghamshire) %>%
  dplyr::filter(!is.na(`Local Authority`))

DT::datatable(boroughs %>% data.frame(check.names = F) %>% select(-geometry), options = list(pageLength=nrow(boroughs), info = FALSE, dom="ft"))
```

Column {data-width=600}
-------------------------------------

### Datatable {data-width=700 .no-padding .no-title}

```{r}


binpal1 <- colorQuantile("YlGnBu", boroughs$`Total public charging devices`, 5)
binpal2 <- colorQuantile("YlGnBu", boroughs$`Total public rapid charging devices`, 5)
binpal3 <- colorQuantile("YlGnBu", boroughs$`Charging devices per 100,000 population`, 5)

boroughs %>%
  leaflet() %>% 
  setView(lat= 54.563652,lng= -5.067734, zoom=6) %>%
  addProviderTiles(providers$Wikimedia) %>% 
  addPolygons(weight=1, color = "white", fillOpacity=0.8, fillColor = ~binpal1(`Total public charging devices`), group="Total CP", popup=~`Local Authority`) %>%
  addPolygons(weight=1, color = "white", fillOpacity=0.8, fillColor = ~binpal2(`Total public rapid charging devices`), group="Total Rapid CP") %>%
  addPolygons(weight=1, color = "white", fillOpacity=0.8, fillColor = ~binpal3(`Charging devices per 100,000 population`), group="Total per Capita") %>%
  addLayersControl(baseGroups=c("Total CP", "Total Rapid CP", "Total per Capita"))

```


About {data-icon="fa-bars"}
===================================== 

#### Ward Reports 

* **Author:** Jack Humble
* **Date Created:** 2020-09-23
* **Date Updated:** `r today()`
* **Email:** jhumble@westminster.gov.uk

This report shows the current and planned EV charge points in Westminster.






