---
title: "Westminster EV Charge Points"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    logo: www/logo.png
    favicon: www/logo.png
    source_code: embed
---

---
# CUSTOM CSS
--- 
<style>                     
.navbar {
  background-color:#2c3e50;
  border-color: black;
}

div .chart-stage .chart-stage-flex {
  padding-left: 0px;
}

.navbar-inverse .navbar-nav>.active>a {
  background-color: #1a242f;
}

.navbar-inverse .navbar-nav>li>a:hover {
  background-color: #1a242f;
}

.navbar-inverse .navbar-nav>.active>a, .navbar-inverse .navbar-nav>.active>a:hover, .navbar-inverse .navbar-nav>.active>a:focus {
  background-color: #1a242f;
}

.nav-tabs-custom > .nav-tabs > li.active {
  border-top-color: #1a242f;
}

.awesome-marker {
  transform: scale(0.5,0.5)
}

.storyboard-nav .sbframelist ul li.active {
    background: #2c3e50;
}

.leaflet-control-layers-expanded {
  color: white;
  background: black;
}

.leaflet .legend i{
  border-radius: 50%;
  width: 10px;
  height: 10px;
  margin-top: 4px;
}

.leaflet-control-attribution {
  display: none;
}

#full_map {
    background: #000;
}  

.legend {
  color: white;
  background: black;
}

.leaflet-popup-content-wrapper, .leaflet-popup-tip {
  background: black;
  color: white;
}
</style> 

```{r setup, include=FALSE}
library(flexdashboard)
library(leaflet)
library(sf)
```

```{r}
west_bord <- sf::read_sf("../../../data/clean_data_files/westminster_boundary_files/London-wards-2018/London-wards-2018_ESRI/London_Ward_CityMerged.shp")
west_bord <- st_transform(west_bord, 4326) 
west_bord <- west_bord %>%
  dplyr::filter(DISTRICT == "City of Westminster")
```


Column {data-width=650}
-----------------------------------------------------------------------

### Chart A {.no-title .no-padding}

```{r}
leaflet() %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  fitBounds(-0.18, 51.495, -0.13, 51.528) %>%
  addPolygons(data=west_bord, fill=TRUE, fillOpacity = 0.3, opacity = 1, fillColor = "white", weight = 1, color = "black", label=~NAME, popup = ~paste(HECTARES, "Hectares"))

```

